Effects of Tunable Hydrophobicity on the Collective Hydrodynamics of Janus Particles under Flows

### 2022-08-05 doc/PRF2022/PRF_main.tex
yny

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Governing Equations: Hydrophobic Attraction Potential Mobility Problem} 
Following the formulation in \citep{Fu2022_JFM}, 
the governing equations are expressed as a system for the position and
orientation of a collection of rigid Janus particles. We first pose the
Stokes equations for the mobility problem giving the hydrodynamic
interactions for the particle suspension. The hydrophobic forces come
from solving a screened Laplace equation. Particle collisions are
avoided through a near-field, pair potential.

@@

Finally, we use the scalar order parameter $S_2$ to quantify the orientational order\cite{Selinger2016}:
\begin{equation}
  \label{eq:S2}
S_2 = \frac{1}{N_b} \sum_{i=1}^{N_b} \frac{1}{2}(3\cos^2(\theta_i - \bar \theta) - 1).
\end{equation}
Here $\bar \theta$ is a circular mean defined as the orientation of the
principal eigenvector of the matrix $\dd_1\dd_1^\top + \cdots +
\dd_{N_b}\dd_{N_b}^\top$. A value $S_2(t) = 1$ indicates that all
particle directors lie on a common axis e.g., two parallel vectors with
possibly opposite direction are ordered. A value below 1 indicates imperfect order, and zero indicates
complete disorder.

@@

\subsection{Bilayer configurations (BC (i)) in a linear shear flow}
To begin, we place the bilayer structure (with BC (i)) from the inset of
Figure~\ref{fig:relax}(b) in a linear shear flow
\begin{equation}
\uu_\infty(\xx) = \dot\gamma \text{ ns }^{-1} ({\bf e}_y \cdot \mathbf{x}) {\bf e}_x,
\end{equation}
%
where $\dot\gamma$ is the dimensionless shear rate, and ${\ee}_x$ and
${\ee}_y$ are horizontal and vertical unit vectors, respectively. The
initial bilayer structure consists of a small self-enclosing bilayer
(vesicle) and several pieces of bilayers.
Figure~\ref{fig:BC1_shear}(a)--(c) shows a snapshot at $t = 0.5$
$\upmu$s of the bilayer for different shear rates $\dot\gamma=
0.05,0.075,0.01$. The dynamics of the bilayer can be found in
Supplementary Movie S2, which shows
that the initial pieces of bilayers
merge and form a worm-like shape under a linear shear flow. At a low
shear rate, the bilayer constantly goes through rotation and extensional
deformation with the whole bilayer remaining intact
(Figure~\ref{fig:BC1_shear}(a)). As the shear rate increases to a
moderate value (Figure~\ref{fig:BC1_shear}(b)), the bilayer is observed
to shed a small piece of bilayer, similar to the asymmetric breakup of a
viscous drop in confinement \cite{DuFuZhuMaLi2016_AICHEJ}.
%\todo[inline]{missing citation}. 
In Figure~\ref{fig:BC1_shear}(c) the high shear rate gives rise to two
separate, nearly equal bilayers, similar to the symmetric drop breakup
under a linear shear flow \cite{Stone1994_ARFM}. 
Refer to Supplementary Movie S4.

@@

We observe that the order parameter $\tilde S_2$ in
Figure~\ref{fig:BC1_shear}(e) is on average increasing. In the initial
configuration, the structure has three or four components.
%
Under the shear flow, the shedding and merging of bilayers results in an
overall decrease in distinct bilayer structures. Similarly, the free
energies are slightly decreasing (Figure~\ref{fig:BC1_shear}(d)), with
the overall changes occurring in the range of a few $\mathrm{k_BT}$/nm.
This suggests that the shear flow changes the energy landscape to move
the local equilibrium obtained from a random initial condition to an
alternate local equilibrium with less free energy and greater
orientational order  (Supplementary Movie S2).  Note that the free energy $F$ in
Figure~\ref{fig:BC1_shear}(d) has the unit of force ($\mathrm{k_BT}$/nm $\approx$ 4.114 pN)
because our system
is two dimensional.
%
%\begin{figure}
%  \begin{center}
%    \includegraphics[width=1.0\textwidth]{Figures/Figure6.pdf}        
%  \end{center}
%\caption{\label{fig:ves_TG} Single vesicle in a TG flow. Panels (a)-(c) are snapshots for $V_0=\{0.1, 0.15, 0.2\}$ at $t=0.6\ \mu$s where the pre-relaxed initial configuration is shown in inset of panel (a). The streamlines are plotted in the background.
%Panel (d) plots the free energies; panel (e) shows orientational parameter $\tilde{S}_2$; panel (f) shows positional parameter E.
%}
%\end{figure}
%
Finally, the strain parameter diverges in the large shear rate cases
(Figure~\ref{fig:BC1_shear}(f))
because the components eventually completely separate and move away from one another
under the shear flow.

@@

%%%%%%%
%
\begin{figure}
  \begin{center}
    \includegraphics[width=1.0\textwidth]{Figures/Figure5.pdf}    
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:BC1_TG} Bilayers with multiple domains in a
  Taylor-Green when $V_0 = \{0.1, 0.15, 0.2\}$ at $t=0.2\ \upmu$s. The
  pre-relaxed initial configuration is shown in the inset of panel (a).
  The streamlines are plotted in the background. Panel (d) shows the
  free energies; panel (e) shows the orientational parameter
  $\tilde{S}_2$; panel (f) shows the positional parameter $E$.}
\end{figure}
%
\subsection{Bilayer and vesicle configurations in a Taylor-Green flow}
Next, we subject the JP structures to the Taylor-Green (TG) background
flow
\begin{equation}
\label{eq:tg_flow}
\uu_\infty(\xx) = V_0\; \frac{\text{nm}}{\text{ns}}\;
\left(
-\cos\left(x/\lambda\right)
 \sin\left(y/\lambda\right)
         {\bf e}_x
         +\sin\left(x/\lambda\right)
         \cos\left(y/\lambda\right)
             {\bf e}_y\right),
\end{equation}
where $x = {\bf e}_x \cdot \xx$ and $y = {\bf e}_y \cdot \xx$
are the horizontal and vertical coordinates, respectively. 
The TG flow is a confining flow consisting of a checkerboard pattern
of cells with alternating circulation. We control the flow by the
dimensionless flow strength $V_0$ and the dimensionless cell size $l$
defining $\lambda = l$ nm. For most of the results in this subsection,
we use the parameter $l=2$.
%

@@

There is no appreciable pattern in the deformation for the
case of bilayers with multiple domains in TG flow
(Supplementary Movie S3, right panel).
Figure~\ref{fig:BC1_TG}(a)--(c)
are the snapshots when $V_0=0.1,0.15,0.2$ at $t = 0.2$ $\upmu$s. At all
flow strengths, the bilayer components are separated and mixed by the
flow in neighboring cells. In the $V_0 = 0.2$ case, the flow breaks off
components consisting of only a few particles, leading an increase in
energy (Figure~\ref{fig:BC1_TG}(d), long dashed curve). There is no
apparente structure to the change in the orientational order. There is an initial
increase in the strain parameter due to component mixing, but the
strains remains bounded since the particles stay confined to the
neighbors of the central cell.

@@

In all cases, the vesicle tank-treads like in the shear flow case. The
direction of the tank-treading, however, varies with the cell size
(Figure~\ref{fig:BTG_Scale}(a)--(d), directed arcs). We attribute this
change in rotational orientation to the total rotational moment of the
cells that the vesicle passes through.

@@

\subsection{Multilamellar and striated configurations in shear and TG flow}
We have simulated particles for the multilamellar (BC (ii)) and striated
(BC (iii)) boundary conditions, in both shear and TG background flow.
The results are qualitatively similar and will be presented in tandem.
For the multilamellar case, we place a 60-particle configuration (inset
of Figure~\ref{fig:BC2_shear}(a)) in shear flows with $\dot\gamma=0.05,
0.1, 0.15$ and in TG flow with flow rates $V_0=0.1, 0.15, 0.2$. For the
striated case, we also place a 60-particle configuration (inset of
Figure~\ref{fig:BC3_shear}(a)) in shear and TG background flows. Here,
somewhat larger rates are required to see appreciable deformations for
this boundary condition: $\dot\gamma=0.1, 0.125, 0.15$ and $V_0=0.2,
0.25, 0.3$, respectively.
The BC (ii) and BC (iii) in shear flow cases are visualized in
the latter half of 
Supplementary Movie S2 (low shear rate) and 
Supplementary Movie S4 (high shear rate), respectively.
The low and high flow rates for TG flow are shown in
the latter half of
Supplementary Movie S3 and 
Supplementary Movie S5, respectively.

@@

In the high shear rate cases ($\dot\gamma=0.15$), both the multilamellar
and striated configurations become disordered. For BC (ii), the lamella
break apart so that individual bilayers are no longer discernible
(Figure~\ref{fig:BC2_shear}(c)). For BC (iii), the stria peel away from
the main body, but remain individually intact
(Figure~\ref{fig:BC3_shear}(c)). Overall, the particles in BC (ii) and
BC (iii) remain bounded and do not drift away in the shear background
flow like for the BC (i) (Figure~\ref{fig:BC1_shear}(c),
Figure~\ref{fig:Ves_shear}(c)).

@@

At large flow rates $V_0$, both configurations depart significantly from
their local equilibrium. The lamella bilayers from BC (ii) break apart,
forming several unlayered bilayer components
(Figure~\ref{fig:BC2_TG}(c)). In BC (iii), the stria also break apart,
but neighboring particles form 'X'-like arrangements
(Figure~\ref{fig:BC3_TG}(d)), resembling the doubly alternating director
equilibrium (Figure~\ref{fig:relax}(d), center, top white rectangle).

@@

\section{Discussion}
Our results were for $N_b = 60$ particles. This particle number was
large enough for the JP to form measurable structures while giving
manageable simulation times (days) on a single computing processor. The
simulation time for $N_b = 198$ in Figure~\ref{fig:relax} and
Figure~\ref{fig:relax_energy} was several weeks, and so we avoided
simulations of this size for our results. We used $N = 16$ grid points
per particle for all simulations. We performed a convergence study and
found that using $N = 16$ or $N = 24$ grid points per particle gave
quantitatively indistinguishable results. The time courses consisted of
$O(10^3)$ time steps with $\Delta t = 0.2$ nm.

The free energy $F$ defined in~\eqref{eq:free_energy} scales with the
boundary data $g$ and repulsion modulus $M$. To remove the degree of
freedom in the boundary data, we scaled all boundary data so that the
square integral of $g$ is independent of the type of boundary condition; BC
(i), (ii), or (iii). This way, for a fixed configuration, the
hydrophobic interaction portion of the free energy (the integral
in~\eqref{eq:free_energy}) converges to $\gamma N_b$ in the limit
$\rho = 0$. This gives a free energy per particle that is independent of
the shape and intensity of the hydrophobic interface. In practice, $\rho
> 0$ is fixed and the JPs assume different configurations. As a result,
the equilibrium energies per particle in our simulations are different
and depend on the boundary condition (Figure~\ref{fig:relax_energy}).
They are about 0.26 $\mathrm{k_BT}$/nm for BC (ii), 0.55
$\mathrm{k_BT}$/nm for BC (i), and 1.4 $\mathrm{k_BT}$/nm for BC (iii).

Next, we suspended JPs in viscous background flows and observed
deformations as a function of flow strength. There were three categories
of boundary conditions---BC (i), BC (ii), and BC (iii)---that formed
bilayer, multilamellar, and striated configurations, respectively. For
BC (i), we considered both an unstructured bilayer and a vesicle
bilayer. The background flows were a linear shear flow and a TG flow.

We can characterize the effective material properties of the JP
structures based on the changes in free energy, orientational order, and
strain as a function of flow strength. Generally, $F$ increases, $\tilde
S_2$ decreases, and $E$ increases with increases in both $\dot \gamma$
and $V_0$, as expected. Structurally, the striated JP configuration for
BC (iii) behaved the most like a rigid body over the flow strengths
tested. For this structure, the deformation measures were constant in
time for shear rates $\dot \gamma$ up to $0.15$ and TG flow rate $V_0$
up to $0.25$ (Figure~\ref{fig:BC3_shear} and Figure~\ref{fig:BC3_TG}).
In contrast, a $25\%$--$50 \%$ smaller value for $\dot \gamma$ or $V_0$ was
required to observe nonrigid deformations for the BC (i) and BC (ii)
cases.

In terms of fluid behavior, the multilamellar (BC (ii)) structure
behaves as a shear thinning fluid while the striated structure (BC (iii))
has a finite yield stress. Qualitatively, the strains for BC (ii)
increases gradually with shear rate (Figure~\ref{fig:BC2_shear}(f)). In
contrast, the strains for BC (iii) are constant over a range of flow
strengths and then increase when the flow strengths are large enough to
deform the body (Figure~\ref{fig:BC3_shear}(f)). To quantify this
behavior, we form 
\begin{align}
\mu_{\text{asm}} = \frac{\dot \gamma}{\dot E} \mu 
\end{align}
as an effective dynamic viscosity of the particle assemblies. The
numerator $\dot \gamma \mu$ gives the force per area provided by the
solvent stresses where $\mu = 1$ mPa s is the solvent viscosity. The
strain rate $\dot E$ of the body is the slope of a linear fit to the
strain curves e.g., in Figure~\ref{fig:BC2_shear}(f).

Calculated viscosities of particle assemblies are shown in
Table~\ref{tbl:bcii_visc}. The middle row gives the solid area fraction
$\phi$; the sum of the rigid particle areas divided by the total area of
the solvent and particle region. We observe that for the multilamellar
structure, $\mu_{\text{asm}}$ decreases with increasing shear rate. The
predicted viscosities of the particle assemblies are on the order of
hundreds of times that of water, consistent with suspension viscosities
for noninteracting particles~\cite{KONIJN201461}. In the case of
striated structures, viscosity is effectively infinite for the lower two
of the shear rates, and then drops to a finite value $\mu_{\text{asm}} =
60$ mPa s when the shear rate reaches $0.15$ ns$^{-1}$.
\begin{table}
  \caption{\label{tbl:bcii_visc} The dynamic viscosity of assemblies
  $\mu_{\text{asm}}$ (mPa s).}
\centering
\begin{tabularx}{0.7\textwidth}{c|X|X|X||X|X|X}
&\multicolumn{3}{c||}{BC (ii)} & \multicolumn{3}{c}{BC (iii)}\\
\hline
  $\dot \gamma$ & 0.05 & 0.10 \quad & 0.15 & 0.100 & 0.125 & 0.15\\
  \hline
  $\phi$ & 0.50 & 0.47 & 0.41 & 0.47 & 0.46 & 0.45 \\
  \hline
  $\mu_{\text{sus}} $ & 401 & 66 & 42 & 2.5e3 & 1.4e3 & 60\\
\hline
\end{tabularx}
\end{table}

@@

Recall from~\eqref{eq:SL_BIE} that $u = \mathcal{D}[\sigma]$.
Then  
\begin{align*}
\nabla_{\zz} u(\zz) \cdot \nnu_{\xx}
&=\nnu_\xx \cdot \nabla_\zz \int_\Gamma \frac{\partial G(\zz-\yy)}{\partial \nnu_\yy}\sigma(\yy) \,\dif s_\yy\\
&=\int_\Gamma \nnu_\xx^\top \left(\nabla_\zz\nabla_\yy^\top  G(\zz-\yy)\right) \nnu_\yy\sigma(\yy)  \,\dif s_\yy\\
  &=-\int_\Gamma \nnu_\xx^\top \left(\nabla_\yy\nabla_\yy^\top G(\zz-\yy)\right)\nnu_\yy\sigma(\yy)\ \dif s_\yy,
\end{align*}
since we can interchange $\nabla_\zz$ with $-\nabla_\yy$.
Following~\cite{Hsiao2008}, \S 1.2,
\begin{align}
\nnu_\xx^\top \left(\nabla_\yy\nabla_\yy^\top G(\zz-\yy)\right)\nnu_\yy
=
-\tt_{\xx}^\top \left(\nabla_\yy\nabla_\yy^\top G(\zz-\yy)\right)\tt_{\yy}
+ \Delta_{\yy}G(\zz-\yy) \tt_{\xx}\cdot \tt_{\yy}.
\end{align}
Then, using that $\Delta_{\yy} G(\zz-\yy) = \rho^{-2} G(\zz-\yy)$,
interchanging $\nabla_\yy$ with $-\nabla_\zz$ once more, and integrating
by parts in arclength $s$, we obtain 
\begin{align*}
\nabla_{\zz} u(\zz) \cdot \nnu_{\xx}
&=-\int_\Gamma  \Delta_\yy G(\zz-\yy) {\bf t}_\xx \cdot   {\bf t}_\yy \sigma(\yy)\ \dif s_\yy
+\int_\Gamma({\bf t}_\xx\cdot\nabla_\yy)({\bf t}_\yy\cdot\nabla_\yy G(\zz-\yy))\sigma(\yy)\ \dif s_\yy\\
&= -\int_\Gamma \frac{1}{\rho^{2}} G(\zz-\yy) {\bf t}_\xx \cdot {\bf t}_\yy \sigma(\yy)\ \dif s_\yy  
-({\bf t}_\xx\cdot\nabla_\zz)\int_\Gamma \frac{\dif}{\dif s_\yy}G(\zz-\yy) \sigma(\yy)\ \dif s_\yy\\
&= -\frac{1}{\rho^2} {\bf t}_\xx\cdot \int_\Gamma G(\zz-\yy){\bf t}_\yy \sigma(\yy)\ \dif s_\yy + 
({\bf t}_\xx \cdot \nabla_\zz)\int_\Gamma G(\zz-\yy)\frac{\dif }{\dif s} \sigma(\yy)  \dif s_\yy.
\end{align*}
%
Letting $\zz\to\xx\in\Gamma$, and noting that both sides of the equation
are continuous, we obtain~\eqref{eq:normal_deriv}.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Governing Equations: Hydrophobic Attraction Potential Mobility Problem} 
Following the formulation in \citet{Fu2022_JFM}, 
the governing equations are expressed as a system for the position and
orientation of a collection of rigid Janus particles. We first pose the
Stokes equations for the mobility problem giving the hydrodynamic
interactions for the particle suspension. The hydrophobic forces come
from solving a screened Laplace equation. Particle collisions are
avoided through a near-field, pair potential.

@@

Finally, we use the scalar order parameter $S_2$ to quantify the orientational order\cite{Selinger2016}:
\begin{equation}
  \label{eq:S2}
S_2 = \frac{1}{N_b} \sum_{i=1}^{N_b} \frac{1}{2}(3\cos^2(\theta_i - \bar \theta) - 1).
\end{equation}
Here $\bar \theta$ is a circular mean defined as the orientation of the
principal eigenvector of the matrix $\dd_1\dd_1^\top + \cdots +
\dd_{N_b}\dd_{N_b}^\top$. Defined as such, $S_2$ is always in the range $0 \le S_2 \le 1$.
A value $S_2 = 1$ indicates that all
particle directors lie on a common axis e.g., two parallel vectors with
possibly opposite direction are ordered. A value below 1 indicates imperfect order, and $S_2=0$ indicates
complete disorder.

@@

\subsection{Bilayer configurations (BC (i)) in a linear shear flow}
To begin, we place the bilayer structure (with BC (i)) from the inset of
Figure~\ref{fig:relax}(b) in a linear shear flow
\begin{equation}
\uu_\infty(\xx) = \dot\gamma \text{ ns }^{-1} ({\bf e}_y \cdot \mathbf{x}) {\bf e}_x,
\end{equation}
%
where $\dot\gamma$ is the dimensionless shear rate, and ${\ee}_x$ and
${\ee}_y$ are horizontal and vertical unit vectors, respectively. The
initial bilayer structure consists of a small self-enclosing bilayer
(vesicle) and several pieces of bilayers.
Figure~\ref{fig:BC1_shear}(a)--(c) shows a snapshot at $t = 0.5$
$\upmu$s of the bilayer for different shear rates $\dot\gamma=
0.05,0.075,0.01$. The dynamics of the bilayer can be found in
Supplementary Movie S2, which shows
that the initial pieces of bilayers
merge and form a worm-like shape under a linear shear flow. At a low
shear rate, the bilayer constantly goes through rotation and extensional
deformation with the whole bilayer remaining intact
(Figure~\ref{fig:BC1_shear}(a)). As the shear rate increases to a
moderate value (Figure~\ref{fig:BC1_shear}(b)), the bilayer is observed
to shed a small piece of bilayer, similar to the asymmetric breakup of a
viscous drop in confinement \cite{DuFuZhuMaLi2016_AICHEJ}.
%\todo[inline]{missing citation}. 
In Figure~\ref{fig:BC1_shear}(c) the high shear rate gives rise to two
separate, nearly equal bilayers, similar to the symmetric drop breakup
under a linear shear flow \cite{Stone1994_ARFM}. For the dynamic evolution, see
Supplementary Movie S4.

@@

We observe that the order parameter $\tilde S_2$ in
Figure~\ref{fig:BC1_shear}(e) is on average increasing. In the initial
configuration, the structure has three or four pieces of bilayer.
%
Under the shear flow, the shedding and merging of bilayers results in an
overall decrease in distinct bilayer structures. Similarly, the free
energies are slightly decreasing (Figure~\ref{fig:BC1_shear}(d)), with
the overall changes occurring in the range of a few $\mathrm{k_BT}$/nm.
This suggests that the shear flow changes the energy landscape to move
the local equilibrium obtained from a random initial condition to an
alternate local equilibrium with less free energy and greater
orientational order  (Supplementary Movie S2).  Note that the free energy $F$ in
Figure~\ref{fig:BC1_shear}(d) has the unit of force ($\mathrm{k_BT}$/nm $\approx$ 4.114 pN)
because our system
is two dimensional.
%
%\begin{figure}
%  \begin{center}
%    \includegraphics[width=1.0\textwidth]{Figures/Figure6.pdf}        
%  \end{center}
%\caption{\label{fig:ves_TG} Single vesicle in a TG flow. Panels (a)-(c) are snapshots for $V_0=\{0.1, 0.15, 0.2\}$ at $t=0.6\ \mu$s where the pre-relaxed initial configuration is shown in inset of panel (a). The streamlines are plotted in the background.
%Panel (d) plots the free energies; panel (e) shows orientational parameter $\tilde{S}_2$; panel (f) shows positional parameter E.
%}
%\end{figure}
%
Finally, the strain parameter diverges in the large shear rate cases
(Figure~\ref{fig:BC1_shear}(f))
because the various pieces of bilayer eventually completely separate and move away from one another
under the shear flow.

@@

%%%%%%%
%
\begin{figure}
  \begin{center}
    \includegraphics[width=1.0\textwidth]{Figures/Figure5.pdf}    
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:BC1_TG} Bilayers with multiple domains in a
  Taylor-Green when $V_0 = \{0.1, 0.15, 0.2\}$ at $t=0.2\ \upmu$s. The
  pre-relaxed initial configuration is shown in the inset of panel (a).
  The streamlines are plotted in the background. Panel (d) shows the
  free energies; panel (e) shows the orientational parameter
  $\tilde{S}_2$; panel (f) shows the positional parameter $E$.}
\end{figure}
%
\subsection{Bilayer and vesicle configurations in a Taylor-Green flow}
Next, we subject the JP structures to a steady Taylor-Green (TG) background
flow
\begin{equation}
\label{eq:tg_flow}
\uu_\infty(\xx) = V_0\; \frac{\text{nm}}{\text{ns}}\;
\left(
-\cos\left(x/\lambda\right)
 \sin\left(y/\lambda\right)
         {\bf e}_x
         +\sin\left(x/\lambda\right)
         \cos\left(y/\lambda\right)
             {\bf e}_y\right),
\end{equation}
where $x = {\bf e}_x \cdot \xx$ and $y = {\bf e}_y \cdot \xx$
are the horizontal and vertical coordinates, respectively. 
The TG flow is a confining flow consisting of a checkerboard pattern
of cells with alternating circulation. We control the flow by the
dimensionless flow strength $V_0$ and the dimensionless cell size $l$
defining $\lambda = l$ nm. For most of the results in this subsection,
we use the parameter $l=2$.
%

@@

There is no appreciable pattern in the deformation for the
case of bilayers with multiple pieces of bilayer in TG flow
(Supplementary Movie S3, right panel).
Figure~\ref{fig:BC1_TG}(a)--(c)
are the snapshots when $V_0=0.1,0.15,0.2$ at $t = 0.2$ $\upmu$s. At all
flow strengths, the bilayer pieces are separated and mixed by the
flow in neighboring cells. In the $V_0 = 0.2$ case, the flow breaks off
bilayers consisting of only a few particles, leading an increase in
energy (Figure~\ref{fig:BC1_TG}(d), long dashed curve). There is no
apparent structure to the change in the orientational order. There is an initial
increase in the strain parameter due to merging and rupture of bilayers, but the
strains remains bounded since the particles stay confined to the
neighbors of the central cell.

@@

In all cases, the JP vesicle tank-treads in TG flow as it does
in the shear flow. The
direction of the tank-treading, however, varies with the cell size
(Figure~\ref{fig:BTG_Scale}(a)--(d), directed arcs). We attribute this
change in rotational orientation to the total rotational moment of the
cells that the vesicle passes through.

@@

\subsection{Multilamellar and striated configurations in shear and TG flow}
We have simulated particles for the multilamellar (BC (ii)) and striated
(BC (iii)) boundary conditions, in both shear and TG background flow.
The results are qualitatively similar and will be presented in tandem.
For the multilamellar (BC (ii)) case, we place a 60-particle configuration (inset
of Figure~\ref{fig:BC2_shear}(a)) in shear flow with $\dot\gamma=0.05,
0.1, 0.15$ and in TG flow with $V_0=0.1, 0.15, 0.2$. For the
striated  (BC (iii)) case, we also place a 60-particle configuration (inset of
Figure~\ref{fig:BC3_shear}(a)) in shear and TG background flows. Here,
somewhat larger rates are required to see appreciable deformations for
this boundary condition: $\dot\gamma=0.1, 0.125, 0.15$ and $V_0=0.2,
0.25, 0.3$, respectively.
The BC (ii) and BC (iii) in shear flow cases are visualized in
the latter half of 
Supplementary Movie S2 (low shear rate) and 
Supplementary Movie S4 (high shear rate), respectively.
The low and high flow rates for TG flow are shown in
the latter half of
Supplementary Movie S3 and 
Supplementary Movie S5, respectively.

@@

In the high shear rate cases ($\dot\gamma=0.15$), both the multilamellar (BC (ii))
and striated (BC (iii)) configurations become disordered. For BC (ii), the lamella
break apart so that individual bilayers are no longer discernible
(Figure~\ref{fig:BC2_shear}(c)). For BC (iii), the stria peel away from
the main body, but remain individually intact
(Figure~\ref{fig:BC3_shear}(c)). Overall, the particles in BC (ii) and
BC (iii) remain bounded and do not drift away in the shear background
flow like for the BC (i) (Figure~\ref{fig:BC1_shear}(c),
Figure~\ref{fig:Ves_shear}(c)).

@@

At large flow rates $V_0$, both configurations depart significantly from
their local equilibrium. The lamella bilayers from BC (ii) break apart,
forming several unlayered bilayer components
(Figure~\ref{fig:BC2_TG}(c)). In BC (iii), the stria also break apart,
but neighboring particles form `X'-like arrangements
(Figure~\ref{fig:BC3_TG}(d)), resembling the doubly alternating director
equilibrium (Figure~\ref{fig:relax}(d), center, top white rectangle).

@@

\section{Discussion\label{sec:discussion}}
Results in \S~\ref{sec:results} are from simulations with $N_b = 60$ particles.
%Our results were for $N_b = 60$ particles. 
This particle number was
large enough for the JP to form measurable structures while giving
manageable simulation times (days) on a single computing processor. The
simulation time for $N_b = 198$ in Figure~\ref{fig:relax} and
Figure~\ref{fig:relax_energy} was several weeks, and so we avoided
simulations of this size for our results. We used $N = 16$ grid points
per particle for all simulations. We performed a convergence study and
found that using $N = 16$ or $N = 24$ grid points per particle gave
quantitatively indistinguishable results. The time courses consisted of
$O(10^3)$ time steps with $\Delta t = 0.2$ ns.

The free energy $F$ defined in~\eqref{eq:free_energy} scales with the
boundary data $g$ and repulsion modulus $M$. 
%To remove the degree of freedom in the boundary data, 
We thus scale all boundary data so that the
square integral of $g$ is independent of the type of boundary condition; BC
(i), (ii), or (iii). This way, for a fixed configuration, the
hydrophobic interaction portion of the free energy (the integral
in~\eqref{eq:free_energy}) converges to $\gamma N_b$ in the limit
$\rho = 0$. This gives a free energy per particle that is independent of
the shape and intensity of the hydrophobic interface. In practice, $\rho
> 0$ is fixed and the JPs assume different configurations. As a result,
the equilibrium energies per particle in our simulations are different
and depend on the boundary condition (Figure~\ref{fig:relax_energy}).
They are about 0.26 $\mathrm{k_BT}$/nm for BC (ii), 0.55
$\mathrm{k_BT}$/nm for BC (i), and 1.4 $\mathrm{k_BT}$/nm for BC (iii).

Next, we impose a flow on the JP suspension to study
deformations of JP assemblies as a function of flow strength. There are three categories
of boundary conditions---BC (i), BC (ii), and BC (iii)---that form
bilayer, multilamellar, and striated configurations, respectively. For
BC (i), we consider both an unstructured bilayer and a vesicle
bilayer. The background flows are a linear shear flow and a steady TG flow.

We characterize the effective material properties of the JP
structures based on the changes in free energy, orientational order, and
strain as a function of flow strength. Generally, $F$ increases, $\tilde
S_2$ decreases, and $E$ increases with increases in both $\dot \gamma$
and $V_0$, as expected. Structurally, the striated JP configuration for
BC (iii) behaves the most like a rigid body over the flow strengths
tested. For this structure, the deformation measures are constant in
time for shear rates $\dot \gamma$ up to $0.15$ and TG flow rate $V_0$
up to $0.25$ (Figure~\ref{fig:BC3_shear} and Figure~\ref{fig:BC3_TG}).
In contrast, a $25\%$--$50 \%$ smaller value for $\dot \gamma$ or $V_0$ is
required to observe nonrigid deformations for the BC (i) and BC (ii)
cases.

In terms of fluid behavior, the multilamellar (BC (ii)) structure
behaves as a shear thinning fluid while the striated structure (BC (iii))
has a finite yield stress. Qualitatively, the strains for BC (ii)
increases gradually with shear rate (Figure~\ref{fig:BC2_shear}(f)). In
contrast, the strains for BC (iii) are constant over a range of flow
strengths and then increase when the flow strengths are large enough to
deform the body (Figure~\ref{fig:BC3_shear}(f)). To quantify this
behavior, we form 
\begin{align}
\label{eq:mu_asm}
\mu_{\text{asm}} = \frac{\dot \gamma}{\dot E} \mu 
\end{align}
as an effective dynamic viscosity of the particle assemblies. The
numerator $\dot \gamma \mu$ gives the force per area provided by the
solvent stresses where $\mu = 1$ mPa s is the solvent viscosity. The
strain rate $\dot E$ of the body is the slope of a linear fit to the
strain curves e.g., in Figure~\ref{fig:BC2_shear}(f).

The viscosities of particle assemblies calculated from \eqref{eq:mu_asm} are shown in
Table~\ref{tbl:bcii_visc}. The middle row gives the solid area fraction
$\phi$; the sum of the rigid particle areas divided by the total area of
the solvent and particle region. We observe that for the multilamellar
structure, $\mu_{\text{asm}}$ decreases with increasing shear rate. The
predicted viscosities of the particle assemblies are on the order of
hundreds of times that of water, consistent with suspension viscosities
for noninteracting particles~\cite{KONIJN201461}. In the case of
striated structures, viscosity is effectively infinite for the lower two
of the shear rates, and then drops to a finite value $\mu_{\text{asm}} =
60$ mPa s when the shear rate reaches $0.15$ ns$^{-1}$.
\begin{table}
  \caption{\label{tbl:bcii_visc} The dynamic viscosity of assemblies
  $\mu_{\text{asm}}$ (mPa s).}
\centering
\begin{tabularx}{0.7\textwidth}{c|X|X|X||X|X|X}
&\multicolumn{3}{c||}{BC (ii)} & \multicolumn{3}{c}{BC (iii)}\\
\hline
  $\dot \gamma$ & 0.05 & 0.10 \quad & 0.15 & 0.100 & 0.125 & 0.15\\
  \hline
  $\phi$ & 0.50 & 0.47 & 0.41 & 0.47 & 0.46 & 0.45 \\
  \hline
  $\mu_{\text{sus}} $ & 401 & 66 & 42 & 2.5e3 & 1.4e3 & 60\\
\hline
\end{tabularx}
\end{table}

@@

Recall from~\eqref{eq:SL_BIE} that $u = \mathcal{D}[\sigma]$.
Then  
\begin{align*}
\nabla_{\zz} u(\zz) \cdot \nnu_{\xx}
&=\nnu_\xx \cdot \nabla_\zz \int_\Gamma \frac{\partial G(\zz-\yy)}{\partial \nnu_\yy}\sigma(\yy) \,\dif s_\yy\\
&=\int_\Gamma \nnu_\xx^\top \left(\nabla_\zz\nabla_\yy^\top  G(\zz-\yy)\right) \nnu_\yy\sigma(\yy)  \,\dif s_\yy\\
  &=-\int_\Gamma \nnu_\xx^\top \left(\nabla_\yy\nabla_\yy^\top G(\zz-\yy)\right)\nnu_\yy\sigma(\yy)\ \dif s_\yy,
\end{align*}
since we can interchange $\nabla_\zz$ with $-\nabla_\yy$.
Following~\citet{Hsiao2008}, \S 1.2,
\begin{align}
\nnu_\xx^\top \left(\nabla_\yy\nabla_\yy^\top G(\zz-\yy)\right)\nnu_\yy
=
-\tt_{\xx}^\top \left(\nabla_\yy\nabla_\yy^\top G(\zz-\yy)\right)\tt_{\yy}
+ \Delta_{\yy}G(\zz-\yy) \tt_{\xx}\cdot \tt_{\yy}.
\end{align}
Then, using that $\Delta_{\yy} G(\zz-\yy) = \rho^{-2} G(\zz-\yy)$,
interchanging $\nabla_\yy$ with $-\nabla_\zz$ once more, and integrating
by parts in arclength $s$, we obtain 
\begin{align*}
\nabla_{\zz} u(\zz) \cdot \nnu_{\xx}
&=-\int_\Gamma  \Delta_\yy G(\zz-\yy) {\bf t}_\xx \cdot   {\bf t}_\yy \sigma(\yy)\ \dif s_\yy
+\int_\Gamma({\bf t}_\xx\cdot\nabla_\yy)({\bf t}_\yy\cdot\nabla_\yy G(\zz-\yy))\sigma(\yy)\ \dif s_\yy\\
&= -\int_\Gamma \frac{1}{\rho^{2}} G(\zz-\yy) {\bf t}_\xx \cdot {\bf t}_\yy \sigma(\yy)\ \dif s_\yy  
-({\bf t}_\xx\cdot\nabla_\zz)\int_\Gamma \frac{\dif}{\dif s_\yy}G(\zz-\yy) \sigma(\yy)\ \dif s_\yy\\
&= -\frac{1}{\rho^2} {\bf t}_\xx\cdot \int_\Gamma G(\zz-\yy){\bf t}_\yy \sigma(\yy)\ \dif s_\yy + 
({\bf t}_\xx \cdot \nabla_\zz)\int_\Gamma G(\zz-\yy)\frac{\dif }{\dif s} \sigma(\yy)  \dif s_\yy.
\end{align*}
%
Letting $\zz\to\xx\in\Gamma$, and noting that both sides of the equation
are continuous, we obtain~\eqref{eq:normal_deriv}.
